\documentclass[12pt]{constitution}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\begin{document}
\title{Cybersecurity Club Constitution}
\author{Daniel Rohwedder}
\date{}
\maketitle
\tableofcontents
\article{The Name of Organization}

The name of the Organization shall be Cybersecurity Club.

\article{Mission and Philosophy}

The mission of the Organization shall be to inform, educate, and create a collaborative learning environment about the multidisciplinary issue of cybersecurity.

The mission of the Organization shall be consistent with the mission of George Fox University.

This Organization shall abide by all applicable rules and regulations of the University.

This Organization shall also abide by the rules and regulations of the University and the Board of Trustees as stated in the George Fox University Student Handbook.

This Organization shall also abide by the rules and regulations stated in the George Fox University Cyber Ethics agreement\footnote{Dr. Wilson, can you provide that document? I want the club to have the same agreement that we had to sign in Secure Software/Digital Forensics}.

\article{Membership}

Membership shall be open to all George Fox University students and must comply with federal laws prohibiting discrimination on the basis of race, sex, handicap, age, sexual orientation, or political or religious affiliation. 
 Compliance with these laws means that membership, benefits, and the election of officers will not be made on the basis of these factors.

Other members of the University community (defined as current faculty, staff, administrators and alumni) may attend the Organization’s meetings and activities but may not conduct business on behalf of the Organization, hold positions of responsibility including but not limited to elected, appointed, or volunteer positions or be involved in the finances of the Organization.

Membership in the Organization shall be determined by attendance at two consecutive meetings of the Organization.

\article{Officers and Duties}

The Officers of the Organization shall consist of a President, Vice President, and Treasurer, who shall constitute the Executive Board of the Organization.

Additional Officer positions may be created and officers appointed by the Executive Board. These shall include but are not limited to operations officers, web master, and committee chairs. The Executive Board may include these appointed officers as part of the Organization’s governing body if a description of their responsibilities and authority are included in the Organization’s Constitution.

Clubs are required to have a full time faculty or staff member as their advisor.

All club officers shall be fully matriculated George Fox University students in good standing with the University.

Any George Fox University student eligible to be an Officer of the Organization shall not be permitted to hold more than one office in that organization at any one time.

\section{President}

The President shall call all meetings of the Membership, regular or otherwise, and shall serve as the chairperson of such meetings. 
In addition, the President shall, with the advice of the Executive Committee, plan and coordinate the events to be sponsored by the Organization in forthcoming terms; with the Treasurer, if applicable prepare and present a regular budget request to the appropriate funding source, and shall serve as a liaison with the ASC Clubs Director, Executive Vice President, ASC Advisor, or any other external administrator(s).

\section{Vice President}

The Vice President, in the absence of the President, or should the President prove unable or unwilling to perform the duties described above, shall assume the responsibilities of the President. 
In addition, the Vice President shall preside overall meetings of the Executive Committee and shall also perform other duties as the President may assign as needed.

\section{Treasurer}

The Treasurer shall be responsible for maintaining accurate financial records of the Organization and shall be allowed to request payment on behalf of the Organization.
The Treasurer, with the President, shall prepare and present any budget requests to the appropriate funding source.


Any Officer of the Organization may resign at any time by delivering a written notice or email of such resignation to the President, or in the case of the resignation of the President, to the Vice President.

When an Officer position is vacated, the Executive Board shall fill the position as quickly as possible, through election or appointment.


The Executive Board shall propose a program of events or publication to be sponsored by the Organization in forthcoming fall and spring semesters.
Proposed programs shall be presented to the Membership for their approval at a general Meeting of the Members of the Organization. 
The Executive Board shall encourage Members to recommend programs or publication to be sponsored by the Organization. 
When appropriate, the Executive Committee shall appoint Members to serve as committee chairs to over see the various tasks related to the program or publication and to solicit the involvement of other Members of the Organization.

\article{Quorum and Meetings}

A quorum shall exist at any Meeting of the Membership where at least fifty percent (50\%) of the Members are in attendance.

Actions requiring a vote may only take place when a quorum is present.
The Vice President shall record the votes and announce the outcome.
They shall also maintain records related to the vote including procedures for voting and the vote count.

All Members shall be notified via E-mail of any Meeting and the nature of the business to be transacted there at least one week before such Meeting. 
\emph{No Meeting shall be called with the intent to exclude any one Member or any portion of the Membership.}

The Executive Committee of the Organization shall meet at least once before any Meeting of the Membership at such time and place to be determined by the President. 
At such Meetings of the Executive Committee a quorum shall be deemed to be the attendance of any three (3) members of the Executive Committee.
The Vice President shall reside over this meeting. 
The President shall reside over the meeting when the Vice President is unable to attend the meeting.

\article{Miscellaneous}

This Constitution may be amended or repealed by a two-thirds (2/3) majority vote of the Members of the Organization.

Any amendment to this Constitution shall be attached hereto and made a part hereof for all purposes.

This Constitution and any amendments and changes hereto shall be filed by the club with ASC and shall be available to any Member of the Organization for inspection during office hours\footnote{Is this true? I would like it to be this way, not sure yet.}.

The Constitution on file in ASC Offices shall be the official Constitution of the organization.

\end{document}
